Why do we Eval?\\[2mm]\Large A large-scale study of Eval usage in R

### 2020-12-18 paper/main.tex
Plots
Fixing figures
ggproto: most of the symbols evaluated

\vspace{-2mm}
\includegraphics[width=.35\textwidth]{calls_per_run_per_call_site}
\vspace{-2mm}
    \caption{Normalized invocations
      (small)} \label{fig:callsitesnormalized}
\vspace{-8mm}
\end{wrapfigure}

@@

Analysis of the arguments passed to \eval reveals that \Symbolpercent
are of kind \c{symbol} (these are single variables such as \c{x}),
\Languagepercent are \c{language} (an internal R type roughly
corresponding to a single expression, such as \c{x+1}), and
\Expressionpercent are \c{expression} (one or more statements). These
account for \Codepercent of the invocations, the arguments to the
remaining invocations are R values which are returned unchanged by
\eval.

To estimate how much executable code is injected into the program
through \eval, we measure the size of arguments in number of
characters. This measurement is obtained by de-parsing every argument
to \eval. Our de-narser does not emit code for values as some values
can be very large and would overwhelm the code. On average, arguments
to \eval are \Avgszeval characters long, the median size is
\Medianszeval. The large input observed is \Maxszeval.
Figure~\ref{fig:sizedistribution} shows the distribution of sizes. The
x-axis is the size of arguments in characters, and the y-axis is the
count of arguments with that size.

@@

\begin{figure}[h!]
	\centering
	\includegraphics[width=.4\textwidth]{events_per_pack_small}
	\includegraphics[width=.4\textwidth]{events_per_pack_large}
	\caption{Events per packages} \label{fig:eventsPerPackage}
\end{figure}

@@

\begin{itemize}
\item Increase font size on numbers for figures
\item change colors on figure 8 (don't like the red)
\item check that on figure 7, the number of elements at 1 is correct
\item explain the peak at 4, for figure 7
\item Figure 8 explain why so few 1's
\item Add a ``Discussion'' paragraph at the end that sums up the
  observations
\item Add paragraphs for Kaggle and CORE -- only discuss the
  differences from CRAN if any.
\item Question: should we remove ggplot? Would change things
  significantly?
\end{itemize}

>>>>

\vspace{-2mm}
\includegraphics[width=7.5cm, trim=7.5cm 0 6cm 0, clip]{calls_per_run_per_call_site}
\vspace{-7mm}
    \caption{Normalized invocations
      (small)} \label{fig:callsitesnormalized}
\vspace{-8mm}
\end{wrapfigure}

@@

Analysis of the arguments passed to \eval reveals that \Symbolpercent
are of kind \c{symbol} (these are single variables such as \c{x}),
\Languagepercent are \c{language} (an internal R type roughly
corresponding to a single expression, such as \c{x+1}), and
\Expressionpercent are \c{expression} (one or more statements).  These
account for \Codepercent of the invocations, the arguments to the
remaining invocations are R values which are returned unchanged by
\eval. Most of the invocations involving a symbol come from ggplot2, \Ggplotsymbolpercent, and from one call site, in \c{ggproto}, evaluating symbol \c{`_inherit`}.

To estimate how much executable code is injected into the program
through \eval, we measure the size of arguments in number of
AST nodes. For instance, a variable name (a symbol) counts for 1 node. Our de-parser does not emit code for values as some values
can be very large and would overwhelm the code. On average, arguments
to \eval are \Avgszeval nodes large, the median size is
\Medianszeval. The largest input observed is \Maxszeval.
Figure~\ref{fig:sizedistribution} shows the distribution of sizes. The
x-axis is the size of arguments in number of nodes, and the y-axis is the
count of arguments with that size.

@@

\begin{figure}[h!]
	\centering
	\includegraphics[width=.55\textwidth]{events_per_pack_small}
	\hspace{-10mm}
	\includegraphics[width=.55\textwidth]{events_per_pack_large}
	\caption{Events per packages} \label{fig:eventsPerPackage}
\end{figure}

@@

\begin{itemize}
\item check that on figure 7, the number of elements at 1 is correct
\item explain the peak at 4, for figure 7
\item Figure 8 explain why so few 1's
\item Add a ``Discussion'' paragraph at the end that sums up the
  observations
\item Add paragraphs for Kaggle and CORE -- only discuss the
  differences from CRAN if any.
\item Question: should we remove ggplot? Would change things
  significantly?
\end{itemize}
